---
title: "Getting Over It"
description: |
  Visualising my Transalp bike ride
author:
  - name: Julian During
date: "`r Sys.Date()`"
output: distill::distill_article
repository_url: https://github.com/duju211/transalp
---

This summer I crossed the alps with my road bike. I've recorded the whole ride
and as a nice memory, I would like to visualise this ride. 

A short time ago I've discovered the awesome R package `drake`.
The use of this package
transformed the way I do my analysis and it helps me to make my post more 
reproducible. The following
[blog post](https://milesmcbain.xyz/the-drake-post/)
describes the underlying workflow, after which I've developed the
underlying package `transalp` for this post.

# Data

At first you have to install the package from github. Then you have to load it. 

```{r eval=FALSE}
remotes::install_github("duju211/transalp")

library(transalp)
```

Load the other necessary libraries:

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(patchwork)
library(drake)
library(here)
library(fs)
```

```{r include=FALSE}
fct_files <- dir_ls("R")

fct_names <- path_file(fct_files) %>% 
  path_ext_remove()

walk2(fct_files, fct_names, ~ knitr::read_chunk(.x, labels = .y))

loadd(gg_altitude_ridges)
loadd(sf_act_meas)
loadd(gg_alpen)
loadd(gg_rides)
```

The package includes the underlying data:

```{r}
df_act_meas_raw <- transalp::df_act_meas
```

```{r, echo=FALSE}
df_act_meas_raw
```

# Preprocessing

Look at the first function:

```{r pre_process_meas}
```

The function does some basic preprocessing on the included activities:

* Turn activity date into character (for easier plotting)
* Normalize altitude and distance

```{r eval=FALSE}
df_act_meas <- pre_process_meas(df_act_meas_raw)
```

Nest the data frame by `id` and `act_date_chr`. Create a new `sf` column with
the geospatial information of the activities:

```{r convert_to_sf}
```

```{r, eval=FALSE}
sf_act_meas <- convert_to_sf(df_act_meas)
```

```{r, echo=FALSE}
sf_act_meas
```


Extract the start point of every tour except for the last one. Extract the end
point for this tour.

```{r extract_poi}
```

```{r, eval=FALSE}
df_poi <- extract_poi(sf_act_meas)
```

# Visualisation

## Altitude

Visualise the altitude data:

```{r vis_altitude_ridge}
```

The function mainly applies the `ggridges::geom_ridgeline` function to the data.
A form of visualisation that I've already used a lot. Its style is 
reminiscent of the famous Joy Division album cover.

```{r, eval=FALSE}
gg_altitude_ridges <- vis_altitude_ridge(sf_act_meas)
```

```{r, echo=FALSE}
gg_altitude_ridges
```


## Spatial Data

Determine the map data for all the activities. Use the `ggmap::get_stamenmap`
function to download the data. The bounding box is calculated from the
`sf_act_meas` object.

```{r get_alpen_map}
```

```{r eval=FALSE}
gg_alpen <- get_alpen_map(sf_act_meas, tol_bbox = 0.1, map_zoom = 9)
```

```{r, echo=FALSE}
ggmap::ggmap(gg_alpen)
```


Plot the activity and the point of interest data onto the map. Use the 
`ggrepel` package to plot the labels of the points of interest. This avoids
too much overplotting.

```{r vis_ride}
```

```{r eval=FALSE}
gg_rides <- vis_ride(sf_act_meas, gg_alpen_map, df_poi)
```

```{r, echo=FALSE}
gg_rides
```

## Combine Visualisations

Combine everything into one big plot using the `patchwork` package:

```{r transalp_plot_final, message=FALSE, preview=TRUE}
# extrafont::font_import()
extrafont::loadfonts(device = "win")

final_plot <- (gg_rides + gg_altitude_ridges) +
      plot_annotation(
        title = "Transalp 2020",
        subtitle = "Albstadt - Lugano") &
      theme(text = element_text(family = "Fira Code Retina"))

final_plot
```

The `extrafont` package helps with using some fancy fonts. The `font_import`
function has to be called once.
Comment the function call in the above code chunk because of this.

