---
title: "Getting Over It"
description: |
  Visualising my Transalp bike ride
author:
  - name: Julian During
date: "`r Sys.Date()`"
output: distill::distill_article
repository_url: https://github.com/duju211/transalp
base_url: https://www.datannery.com/posts/transalp/
creative_commons: CC BY
params:
  interactive: TRUE
  gg_ride: "transalp.png"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
source("libraries.R")

df_manifest_raw <- tar_manifest()
df_manifest <- df_manifest_raw |>
  mutate(command = str_glue("{name} <- {command}"))

knitr::opts_chunk$set(eval = !params$interactive)
```


In summer 2020, I crossed the alps with my road bike.
I've recorded the whole ride
and as a nice memory, I would like to visualise this ride. 

# Data

Load the other necessary libraries:

```{r}
#| file="libraries.R",
#| eval=FALSE
```

Define where activity data is read from:

```{r act_file}
#| code=df_manifest$command[df_manifest$name == "act_file"]
```

```{r meas_file}
#| code=df_manifest$command[df_manifest$name == "meas_file"]
```

Read activity data from rds file. Define point of interests names and
define if it should be mapped to the start or the end of the activity:

```{r}
#| file="R/act.R"
```

```{r df_act}
#| code=df_manifest$command[df_manifest$name == "df_act"]
```

Read meas data:

```{r}
#| file="R/meas.R"
```

```{r df_meas}
#| code=df_manifest$command[df_manifest$name == "df_meas"]
```

Turn measurements into sf object:

```{r}
#| file="R/act_meas_points.R"
```

```{r}
#| code=df_manifest$command[df_manifest$name == "sf_act_meas_points"]
```

Combine into one LINESTRING:

```{r}
#| file="R/act_meas_lines.R"
```

```{r sf_act_meas}
#| code=df_manifest$command[df_manifest$name == "sf_act_meas_lines"]
```

Read raster data:

```{r}
#| file="R/alpen_raster.R"
```

```{r raster_alpen}
#| code=df_manifest$command[df_manifest$name == "raster_alpen"]
```

# Visualisation

```{r}
#| file="R/vis_ride.R"
```

```{r gg_ride}
#| code=df_manifest$command[df_manifest$name == "gg_ride"]
```

```{r, echo=FALSE, eval=TRUE}
if (params$interactive) {
  knitr::include_graphics(params$gg_ride)
} else {
  knitr::include_graphics(gg_ride)
}
```

What a ride it has been! I'm always thinking back to this experience.
It's time to recreate such a ride in the near future.
